\textls[-0]{\thetitle}

### 2023-03-04 casestudies.tex
All the stuff from reviewer.

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
the two abstract interpreters in \lsti{ImpTI} and \lsti{ImpCP} are
ready for program extraction to OCaml.
We put the verified abstract interpreters to test over several simple queries. % Reviewer D : l899

>>>>

Our implementation of family polymorphism retains the
ability of program extraction in Coq;
the two abstract interpreters in \lsti{ImpTI} and \lsti{ImpCP} are
ready for program extraction to OCaml.
We put the verified abstract interpreters to test over several simple queries. % Reviewer D : l899

### 2023-03-04 coqimpl.tex
All the stuff from reviewer.

\item
In \cref{fig:stlc-compiled},
an inductive type \lsti{tm} is generated, instantiating the axiomatized
\lsti{tm} type and its constructors.
%
The partial recursor \lsti{tm_prect_STLC} is defined
%to \lsti{\lambda}\,\lsti{P, tm_rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm_rect}, the recursor Coq generates for \lsti{tm}.
Computational behaviors of \lsti{tm_prect_STLC} are immediate, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm_rect}
to the (already included) case handlers. %(\lsti{subst\_tm_unit}, etc.).
Computational behaviors of \lsti{subst} are then immediate, by \lsti{reflexivity}.

>>>>

\item
In \cref{fig:stlc-compiled},
an inductive type \lsti{tm} is generated, instantiating the axiomatized
\lsti{tm} type and its constructors.
%
The partial recursor \lsti{tm_prect_STLC} is defined
%to \lsti{\lambda}\,\lsti{P, tm_rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm_rect}, the recursor Coq generates for \lsti{tm}.
The computational behaviors of \lsti{tm_prect_STLC} are immediate, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm_rect}
to the (already included) case handlers. %(\lsti{subst\_tm_unit}, etc.).
The computational behaviors of \lsti{subst} are then immediate, by \lsti{reflexivity}.

### 2023-03-04 lang-design.tex
Change according to Reviewer Please Review!!!
All the stuff from reviewer.

\cref{fig:stlc-mechanized} shows how STLC and its extension with
fixpoints can be mechanized using \Lang, in a style envisioned in
\cref{fig:stlc-nonmechanized}.
The base family "STLC" hosts the STLC metatheories, from abstract syntax
to the type-safety theorem.
Family "STLCFix", derived from "STLC", makes adjustments as needed by a fixpoints extension:
it adds new constructors to the inductive types (\lsti{FInductive}) and
adds new cases to the recursive functions (\lsti{FRecursion}) and
induction proofs (\lsti{FInduction}).
Existing constructors and cases, as well as those definitions and
theorems that need no adjustments ("ty", "env", "empty", "steps", and
"typesafe"), are automatically inherited and reused.
In particular, executing the last command, \lsti{Check STLCFix.typesafe},
displays the type-safety theorem of the fixpoints extension.

@@

In family "STLCFix", inductive type "tm" \emph{further binds} the "tm" type
in family "STLC". It has five constructors: four inherited from
"STLC" and a fifth called "tm_fix".

@@

With inductive types made extensible, exhaustivity of induction becomes
in jeopardy, however.
In particular, recursor "tm_rect" should no longer be allowed, because
its type mentions "tm", whose meaning is late bound, yet
"tm_rect" purports to claim \lsti{\forall t, P t} given only four case handlers.

@@

Note that the requirement still allows a derived family to introduce
new declarations into the context of a field. %\EDJ{Maybe a better wording is ``the relative order between fields are preserved during inheritance''?}
For example, the left column of \cref{fig:stlc-isorec-prod} shows an
extension of STLC with iso-recursive types, where "tysubst" is
introduced into the context of "hasty".
%
In the event that \Lang cannot infer where the programmer intends to place a new field,
annotation is required.

>>>>

\cref{fig:stlc-mechanized} shows how STLC and its extension with
fixpoints can be mechanized using \Lang, in a style envisioned in
\cref{fig:stlc-nonmechanized}, directly adopted from \citet{sf-pl}. % Review B.244 - mention non-capture avoiding, SF is using non-capture avoiding.
The base family "STLC" hosts the STLC metatheories, from abstract syntax
to the type-safety theorem.
Family "STLCFix", derived from "STLC", makes adjustments as needed by a fixpoints extension:
it adds new constructors to the inductive types (\lsti{FInductive}) and
adds new cases to the recursive functions (\lsti{FRecursion}) and
induction proofs (\lsti{FInduction}).
Existing constructors and cases, as well as those definitions and
theorems that need no adjustments ("ty", "env", "empty", "steps", and
"typesafe"), are automatically inherited and reused.
In particular, executing the last command, \lsti{Check STLCFix.typesafe},
displays the type-safety theorem of the fixpoints extension.

@@

In family "STLCFix", the inductive type "tm" \emph{further binds} the "tm" type
in family "STLC". It has five constructors: four inherited from
"STLC" and a fifth called "tm_fix".

@@

With inductive types made extensible, exhaustivity of induction becomes
in jeopardy, however.\EDJ{``Becomes in jeopardy'' looks weird to me. how about changing to "is now in question"}
In particular, the recursor "tm_rect" should no longer be allowed, because
its type mentions "tm", whose meaning is late bound, yet
"tm_rect" purports to claim \lsti{\forall t, P t} given only four case handlers.

@@

Note that the requirement still allows a derived family to introduce
new declarations into the context of a field. %\EDJ{Maybe a better wording is ``the relative order between fields are preserved during inheritance''?}
For example, the left column of \cref{fig:stlc-isorec-prod} shows an
extension of STLC with iso-recursive types, where "tysubst" is
introduced into the context of "hasty".
%
In the event that \Lang cannot infer where the programmer intends to place a new field,
an annotation is required.

### 2023-03-04 metatheory-condensed.tex
All the stuff from reviewer.

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families; they are like tuples composed of the fields,
with field names represented by variable bindings.
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.

@@

Well-formedness judgments of \emph{linkage signatures} have form
$\goodSig{\Gm}{\lsig}{n}$.
As rules \ruleref{lsig/empty} and \ruleref{lsig/add} show, a linkage
signature is a list of $n$~types.
%
Well-formedness judgments of \emph{linkages} have form $\goodTerm{\Gm}{\lkg}{\TyLkg{\lsig}}$,
where $\TyLkg{\lsig}$ is a type formed by~$\lsig$.
As rules \ruleref{l/empty} and \ruleref{l/add} show, a linkage is a list
of $n$~terms, each representing a field of the family modeled by the linkage.

>>>>

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families; they are like tuples composed of fields,
with field names represented by variable bindings.
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.

@@

Well-formedness judgments of \emph{linkage signatures} have the form
$\goodSig{\Gm}{\lsig}{n}$.
As rules \ruleref{lsig/empty} and \ruleref{lsig/add} show, a linkage
signature is a list of $n$~types.
%
Well-formedness judgments of \emph{linkages} have the form $\goodTerm{\Gm}{\lkg}{\TyLkg{\lsig}}$,
where $\TyLkg{\lsig}$ is a type formed by~$\lsig$.
As rules \ruleref{l/empty} and \ruleref{l/add} show, a linkage is a list
of $n$~terms, each representing a field of the family modeled by the linkage.
